---
title: "Project-2019 NBA"
author: "Group C1"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(plotly)
library(tidyverse)
```

``` {r, echo=FALSE}
# load and clean data sets
games_data <- read.csv("data/games.csv", stringsAsFactors = FALSE)
games_data_2019 <- games_data %>%
  filter(SEASON == "2019")
teams_data <- read.csv("data/teams.csv", stringsAsFactors = FALSE)
teams_data <- teams_data %>%
  select(TEAM_ID, NICKNAME)

# add team names for home teams
teams_data <- teams_data %>%
  rename(HOME_TEAM_ID = TEAM_ID)
add_home_team_name <-
  left_join(games_data_2019, teams_data, by = "HOME_TEAM_ID") %>%
  rename(HOME_TEAM_NAME = NICKNAME)

# add team names for visitor teams
teams_data <- teams_data %>%
  rename(VISITOR_TEAM_ID = HOME_TEAM_ID)
games_data <-
  left_join(add_home_team_name, teams_data, by = "VISITOR_TEAM_ID") %>%
  rename(VISITOR_TEAM_NAME = NICKNAME)
```

```{r echo = FALSE, include=FALSE}
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
source("scripts/Summary information.R")
source("scripts/Summary table.R")
library(knitr)
```

## Introduction
This project takes in a data set of 2019 NBA games. We analyzed 30 teams' performance based on scores, field goal percentage, 3 pointer percentage and other statistics throughout the season. Our group share the same interest in basketball, and we believe the analysis and visualization on the data set could be helpful for us to understand more about each team.

## Summary Information
``` {r, echo=FALSE, include=FALSE}
summary_info <- summary_info(games_data)
```
From the data set, we want to analysis what factors could influence players' performances. Whether home or away games affect players' performances due to changing audiences and environment or is there any other factor? 

From the 2019 NBA season data set, the average field goal percentage for away games is `r summary_info$ave_fg_ptc_away`, which is almost the same as home games `r summary_info$ave_fg_ptc_home`. In comparison to field goal percentage, rebound times is also not significantly different. The number of rebound for home games is `r summary_info$rebound_home`, and the number of rebound for away games is `r summary_info$rebound_away`. Also, because of the COVID, there was a gap between March to July with missing data in 2019 season. This might cause the data not significantly different enough. 

Although there is no significant difference between the home and away games' shooting percentage and rebound times, `r summary_info$num_home_win` home game wins is larger than `r summary_info$num_home_loss` home game losses. Therefore, there might be other factors that influence players' performances. 

## Summary Table
The table shows the sum of each team's three statistics in 2019 season. From the table, we can predict the top teams that may compete during the championship. Because there are four factors affect basketball success, the table below contains three out of four factors for each team's home games. The common sense is that teams with highest field goal percentage, free throw percentage, and rebounds will win the championship. As the data shows, Lakers had the highest field goal percentage and rebounds. They also had second highest free throw percentage, only one percent lower than the highest. Last year's NBA championship was Lakers. The result matches with data in the summary table.
``` {r, echo=FALSE}
kable(summary_table(games_data))
```

## Three Charts

### 1. Double Bar Chart: Top 8 teams FG percentage home vs. away game

``` {r, echo=FALSE, warning=FALSE}
chart1(games_data)
```
This chart was intended to visualize and compare how top 8 teams who have the highest Field Goal percentage in general perform in their home and away games. The grouped bar chart shows clearly the difference between each team's Field Goal percentage in their home and away games.

**Insights:**

* In general, all top8 teams have average field goal percentage higher than 45%
in both home and away games.
* 7 out of top 8 teams have a higher average field goal percentage in home games.
* Pelicans is the only team that has a higher average field goal percentage in
away games, however, the difference is really small, around 0.2%.


### 2. Scatter plot: Lakers 3 Point Percentage:Points
``` {r, echo=FALSE, warning=FALSE}
chart2(games_data)
```
The purpose of this chart was to visuzlize the relationship between the points the Lakers, who won the NBA Title in 2019, scored and their 3 point percentage. The league average on 3 point percentage and points is also plotted to show how much better the Lakers are in each of these categories. The goal of this plot was to see if the Lakers' 3 point percentage was to blame for their success in the 2019 season.

**Insights**

The data in this plot seems to be pretty evenly distributed around the league average which may tell that, in terms of the ratio of 3 point percentage to points, the Lakers are fairly average. They may have found success in other areas to lead them to an NBA title.

### 3. Line Chart: champion team’s (Lakers) PTS throughout the whole season

``` {r echo=FALSE}
chart3(games_data)
```

**Interpretation:**

This chart is try to figure out how many points the 2019 champion, Lakers, get for each game throughout the whole season. Is the champion team perform steady?

We choose the line chart for this problem because it can display the trend clearly. The more closer to the red smooth line, the more steady they perform. However, in season 2019, they were not that steady and have a big range of PTS. The max PTS is above 140, but the minimum they got was less than 80. They may suffer some effect, like player injury or BLM activities. From late March to August, there is a straight line since NBA suspended the games due to the Covid-19. Even though their PTS is not steady, their average PTS is about 110 per game, which is really good and lead them to the final championship.
